Topics in Algorithms

### 2018-01-10 project/paper.tex
Added theorem

The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$. $bdist_k$ uses a binary search, in which $\mathcal{I}$ is halved in size at each recursion and only one of the halves is recursed upon. As the height of the tree is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time. This can be improved to $O(k)$ by constructing of a recursive tree $\mathcal{T}_u$ for each $u$ that represents the recursion of $bdist_k$ on the subsequence $\mathcal{I}'$ consisting of all even numbers in $\mathcal{I}$. A bottom-up seach of $\mathcal{T}_u$ can identify for each canonical subsequence (canonical meaning it is a node in $\mathcal{T}$) $i_1,i_1+2,...,i_2$ an index $j$ in the subsequence that maximizes $\delta_j(u)$ in $O(k)$ time. The bottom-up traversal of $T$ requires checking at most $O(\log k)$ subsequences; consider the subsequence $i_1,..,i_2$ in seperate leaf nodes as seen in Fig. \ref{tree}. The path $P$ (red) starting in $p(l_1)$ and ending in $p(l_2)$ has $O(\log k)$ children, which we denote $X$. The union of $X$ clearly covers the entire subsequence $i_1,i_1+2,...,i_2-2,i_2$, and finding a $j$ that maximizes $\delta_j(u)$ in $X$ therefore gives a $j$ that maximizes $\delta_j(u)$ in the subsequence $i_1,...,i_2$. If $j$ is known for each node in $\mathcal{T}$, it follows that finding the desired $j$ for any canonical subsequences is bound by $O(\log k)$\\

>>>>

The query time is bounded by the number of recursions needed before reaching a $(u,v)-feasible$ subsequence of size at most $\log k$. $bdist_k$ uses a binary search, so that at an arbitraty iteration the subsequence will be split in half into subsequences $i_1,...,i$ and $i,...,i_2$. Only the one of these two subsequences that is $(u,v)$-terminal is then recursed upon. As the number of recursions in this binary search is $O(\log k)$ and $i$ and $j$ are known for all subsequences, the query time is $O(\log k)$.
To bound the time to identify these desired $j$, a simple linear search requires $O(k\log k)$ time. This can be improved to $O(k)$ by constructing of a recursive tree $\mathcal{T}_u$ for each $u$ that represents the recursion of $bdist_k$ on the subsequence $\mathcal{I}'$ consisting of all even numbers in $\mathcal{I}$. A bottom-up seach of $\mathcal{T}_u$ can identify for each canonical subsequence (canonical meaning it is a node in $\mathcal{T}$) $i_1,i_1+2,...,i_2$ an index $j$ in the subsequence that maximizes $\delta_j(u)$ in $O(k)$ time. The bottom-up traversal of $T$ requires checking at most $O(\log k)$ subsequences; consider the subsequence $i_1,..,i_2$ in seperate leaf nodes as seen in Fig. \ref{tree}. The path $P$ (red) starting in $p(l_1)$ and ending in $p(l_2)$ has $O(\log k)$ children, which we denote $X$. The union of $X$ clearly covers the entire subsequence $i_1,i_1+2,...,i_2-2,i_2$, and finding a $j$ that maximizes $\delta_j(u)$ in $X$ therefore gives a $j$ that maximizes $\delta_j(u)$ in the subsequence $i_1,...,i_2$. If $j$ is known for each node in $\mathcal{T}$, it follows that finding the desired $j$ for any canonical subsequences is bound by $O(\log k)$\\
